### 2023-07-26 README.Rmd
IMplemented incremental HS score logging and meta-rule flags.
Revised treament of outputs and HS.
Generalized compare-scenarios. Added tasphaseplot to kobe plots.

>>>>

* 2023-07-26 aMSE 0.1.9 Added tasphaseplots to the kobe plots for comparison.

* 2023-07-24 aMSE 0.1.8 Revised use of TasHS and of comparescenarios, meta-rule flagging now working correctly.

* 2023-07-20 aMSE 0.1.7 Implemented the use of incremental updates of HS scores in a jurisdiction generic manner. Added a meta-rule flagging system.
